---
title: "Solar Adoption in New Jersey"
output: 
  flexdashboard::flex_dashboard:
    theme: darkly
    orientation: rows
    source_code: "https://github.com/psimran-singh/Data-Visualization-Final-Project"
    vertical_layout: fill
runtime: shiny

---
```{r global, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(plotly)
library(formattable)
library(DT)
library(lubridate)
library(xts)
library(dygraphs)
library(nivocal)

# Load in all the data we need
setwd("~/GitHub/Data-Visualization-Final-Project/Data Files for Analysis")
trend <- read_csv('Trend.csv')
totals <- read_csv('kw_co2_conversions.csv')


```


Overall Trends
=====================================

<!-- Solar Energy in New Jersey {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->
<!-- Placeholder - Talk about some stuff -->

Row
-----------------------------------------------------------------------

### Total Current Installed Solar Capacity

```{r}
renderValueBox({
  total_cap <- paste(prettyNum(totals[1,2]/1000,big.mark=",",digits=0)," MW")
  valueBox(total_cap, 
           icon = "fa-sun")
})
```

### Total Metric Tons of CO~2~ Emissions Avoided

```{r}
renderValueBox({
  total_co2 <- paste(prettyNum(totals[1,3],big.mark=","))
  valueBox(total_co2,
           icon = "")
})
```


### Total Passenger Cars Taken Off the Road for 1 Year

```{r}
renderValueBox({
  total_cars <- prettyNum(totals[1,4],big.mark=",")
  valueBox(total_cars,
           icon = "")
})
```

### Total Tree Seedlings Grown for 10 Years

```{r}
renderValueBox({
  total_trees <- prettyNum(totals[1,5],big.mark=",")
  valueBox(total_trees,
           icon = "")
})
```

Row {.tabset}
-----------------------------------------------------------------------

### Cumulative Capacity Trend

```{r}
fig1 <- plot_ly(trend, x = ~Year, y = ~`Residential Capacity (Cumulative)`,
               type = 'bar', name = 'Residential') %>% 
  add_trace(y = ~`Non-Residential Capacity (Cumulative)`, name = 'Non-Residential') %>%
  add_trace(y = ~`Grid Supply Capacity (Cumulative)`, name = 'Grid Supply') %>%
  layout(yaxis = list(title = "Capacity (MW)"), 
         xaxis = list(title = "Year", tickangle = -45, tickmode = 'linear'),
         barmode='stack')
fig1
```

### Yearly Capacity Growth Trend

```{r}
fig2 <- plot_ly(trend, x = ~Year, y = ~`Residential Capacity`,
               type = 'bar', name = 'Residential') %>% 
  add_trace(y = ~`Non-Residential Capacity`, name = 'Non-Residential') %>%
  add_trace(y = ~`Grid Supply Capacity`, name = 'Grid Supply') %>%
  layout(yaxis = list(title = "Capacity (MW)"), 
         xaxis = list(title = "Year", tickangle = -45, tickmode = 'linear'),
         barmode='stack')
fig2
```

### Cumulative Quantity Trend

```{r}
fig3 <- plot_ly(trend, x = ~Year, y = ~`Residential Quantity (Cumulative)`,
               type = 'bar', name = 'Residential') %>% 
  add_trace(y = ~`Non-Residential Quantity (Cumulative)`, name = 'Non-Residential') %>%
  add_trace(y = ~`Grid Supply Quantity (Cumulative)`, name = 'Grid Supply') %>%
  layout(yaxis = list(title = "Quantity"), 
         xaxis = list(title = "Year", tickangle = -45, tickmode = 'linear'),
         barmode='stack')
fig3
```

### Yearly Quantity Growth Trend

```{r}
fig4 <- plot_ly(trend, x = ~Year, y = ~`Residential Quantity`,
               type = 'bar', name = 'Residential') %>% 
  add_trace(y = ~`Non-Residential Quantity`, name = 'Non-Residential') %>%
  add_trace(y = ~`Grid Supply Quantity`, name = 'Grid Supply') %>%
  layout(yaxis = list(title = "Quantity"), 
         xaxis = list(title = "Year", tickangle = -45, tickmode = 'linear'),
         barmode='stack')
fig4
```




Current Landscape by County
=====================================

<!-- Solar Energy in New Jersey {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->
<!-- Placeholder - Talk about some stuff -->

Row
-----------------------------------------------------------------------

### Total Current Installed Solar Capacity

```{r}
renderValueBox({
  total_cap <- paste(prettyNum(totals[1,2]/1000,big.mark=",",digits=0)," MW")
  valueBox(total_cap, 
           icon = "fa-sun")
})
```

### Total Metric Tons of CO~2~ Emissions Avoided

```{r}
renderValueBox({
  total_co2 <- paste(prettyNum(totals[1,3],big.mark=","))
  valueBox(total_co2,
           icon = "")
})
```


### Total Passenger Cars Taken Off the Road for 1 Year

```{r}
renderValueBox({
  total_cars <- prettyNum(totals[1,4],big.mark=",")
  valueBox(total_cars,
           icon = "")
})
```

### Total Tree Seedlings Grown for 10 Years

```{r}
renderValueBox({
  total_trees <- prettyNum(totals[1,5],big.mark=",")
  valueBox(total_trees,
           icon = "")
})
```


Current Residential Landscape
=====================================



Current Landscape by County
=====================================
